Enabling conditions for effective community-based marine reserves in small-scale fisheries

### 2018-04-03 docs/paper/Villasenor-Derbez.Rmd
Added render date to PDF

@@

```{r, results = "asis"}
L_conapesca <- tibble(UnidadEconomica = c("Scpp buzos y pescadores de la baja california scl",
                                          "Scpp cozumel scl",
                                          "Scpp jose maria azcorra scl"),
                      Comunidad = c("Isla Natividad",
                                    "Maria Elena",
                                    "Punta Herrero")) %>% 
  left_join(conapesca, ., by = "UnidadEconomica") %>% 
  mutate(Post = case_when(Comunidad == "Isla Natividad" && Ano <= 2006 ~ 0,
                          Comunidad == "Maria Elena" && Ano <= 2012 ~ 0,
                          Comunidad == "Punta Herrero" && Ano <= 2013 ~ 0,
                          TRUE ~ 1))

C_IN <- filter(L_conapesca, Comunidad == "Isla Natividad") %>% 
  lm(PesoVivo/1000~Post, data = .)

@@

>>>>

**Last_update**: `r Sys.Date()`

@@

```{r, results = "asis"}
C_IN <- filter(L_conapesca, Comunidad == "Isla Natividad") %>% 
  lm(PesoVivo/1000~Post, data = .)

@@

```{r}
invert %>%
  filter(generoespecie == "Panulirus interruptus",
         abundancia < 100) %>% 
  abundance(com = "Isla Natividad") %>%
  mutate(ano = as.numeric(ano)) %>%
  ggplot(aes(x = ano, y = indicador, color = zona)) +
  geom_jitter(height = 0, alpha = 0.5) +
  stat_summary(geom = "line", fun.y = mean) +
  scale_color_brewer(palette = "Set1")
```
